---
title: "Tabulating Results of Simulation Study"
author: "Michael Flanagin  \\ flanna@uw.edu"
date: "August 10, 2018"
classoption: portrait
header-includes:
  - \usepackage[table]{xcolor}
  - \usepackage{booktabs}
  - \usepackage{caption}
output:
  pdf_document:
    fig_caption: yes
    keep_tex: yes
    number_sections: yes
  html_document:
    fig_caption: yes
    force_captions: yes
    highlight: pygments
    number_sections: yes
    theme: cerulean
csl: mee.csl
---
\captionsetup[table]{ labelformat = empty } <!-- disable auto table numbering with kable -->

```{r setup, eval = FALSE, echo=FALSE}
  devtools::install_github("cboettig/knitcitations@v1")
  library(knitcitations); cleanbib()
  cite_options(citation_format = "pandoc", check.entries=FALSE)
  library(bibtex)
```

```{r globalopts, cache = TRUE, warning = FALSE, echo = FALSE}
# Load libraries necessary for functions used in this document
library('knitr')
library('xtable')
library('kableExtra')  # for additional table formatting
# library('dplyr')  # for table coloring
# Set global chunk options
opts_chunk$set(echo = FALSE,     # do NOT repeat code in final document
               message = FALSE,  # do NOT print R messages in document
               warning = FALSE,  # do NOT print warnings
               self.contained = TRUE ) # do NOT call other .Rnw docs! 
round_digits <- 3  # digits to round to when presenting results
options( knitr.table.format = "latex")  # guarantees 'kableExtra' formatting handled properly
options( scipen = 999 )
#         knitr.kable.na = " - ", 
#         scipen = 10)  # replaces NA entries with ' - ' in kable output
#         scipen = 999 )  # effectively disables scientific notation
setwd(getwd())  # set working directory to current file path.

# function kable_booktabs_linesep()
kable_booktabs_linesep <- function( nlines = 6 ){
  #' input: 
  #'   nlines := number of lines per block of table rows
  #' output:
  #'   [character] linespace string to pass to kable()
  #' example:
  #'   kable( foo_table, booktabs = TRUE, linesep = kable_booktabs_linesep( nlines = 6) )
  return(c(rep( '', nlines - 1 ), "\\addlinespace"))
}
```

```{r load_datasets, cache = TRUE, echo = FALSE, message = FALSE}
datadir_path <- "/Users/Moschops/Documents/MSThesis/results/"
#' [ Batch 1 of 4: binary Y, binary X ] 
metrics_batch1 <- read.csv(paste0( datadir_path, "metrics-alloc-simulation-batch-1-of-4.csv" ))
#' [ Batch 2 of 4: binary Y, continuous X ] 
metrics_batch2 <- read.csv(paste0( datadir_path, "metrics-alloc-simulation-batch-2-of-4.csv" ))
#' [ Batch 3 of 4: continuous Y, binary X ] 
metrics_batch3 <- read.csv(paste0( datadir_path, "metrics-alloc-simulation-batch-3-of-4.csv" ))
#' [ Batch 4 of 4: continuous Y, continuous X ] 
metrics_batch4 <- read.csv(paste0( datadir_path, "metrics-alloc-simulation-batch-4-of-4.csv" ))

#' [ Batch 1 of 4: binary Y, binary X -- subsetted on simulations without complete/quasi separation ]
metrics_batch1_sub <- read.csv(paste0( datadir_path, "metrics-subset-alloc-simulation-batch-1-of-4.csv" ))
#' [ Batch 2 of 4: binary Y, continuous X -- subsetted on simulations without complete/quasi separation ]
metrics_batch2_sub <- read.csv(paste0( datadir_path, "metrics-subset-alloc-simulation-batch-2-of-4.csv" ))

```

# Introduction
Simulation results are presented by outcome and predictor variable type pairs (binary, continuous).

Each outcome/predictor pair, we present tables for:

* coverage probability, 
* bias, and 
* power.

Simulation conditions are ordered by:

* sample size (n), 
* marginal outcome prevalence Pr( Y ),
* prognostic factor prevalence Pr( X ),
* treatment effect size (exp( bZ )), and
* prognostic factor effect size (bX).

Binary outcomes are fit with a Binomial generalized linear model, continuous outomes with an ordinary linear model.

Resulting estimates of treatment effect are adjusted ('adj') or unadjusted ('unadj') for prognostic factors used in the allocation method.

Three allocation methods are compared to each other:

* Complete randomization (CR),
* Stratified block randomization (SBR), with a block size of 4,
* Covariate adaptive allocation (CAA), with a maximum imbalance of 2 and an allocation biasing probability of 0.70.

The analysis method for uncertainty estimates is either:

* Model-based (using p-values from relevant t-statistics), or
* Rerandomization-based, with 500 rerandomized treatment allocations performed per simulation draw.

----------

```{r batch-1-binY-binX_bias_examples, cache = TRUE, echo = FALSE, message = FALSE}
cat("Batch 1: bias (no subsetting)\n")
with( metrics_batch1, summary( bias ))
cat("Batch 1: bias (final subsetting)\n")
with( metrics_batch1_sub, summary( bias ))
cat("Batch 2: bias (no subsetting)\n")
with( metrics_batch2, summary( bias ))
cat("Batch 2: bias (final subsetting)\n")
with( metrics_batch2_sub, summary( bias ))
```

```{r assert_that, cache = FALSE, echo = TRUE}
#' [ assert_that( expr, errmsg ) returns `errmsg` if expr is NOT true ]
assert_that <- function( expr, errmsg ){
  if( !all( expr ) )
    stop( errmsg, call. = FALSE )
}

```
Here we define make_summary_table().
```{r summary_table, cache = FALSE, echo = TRUE}
make_summary_table <- function( metric_df = metrics_batch1,
                                metric = "coverage",
                                get_adj_ests = TRUE,
                                round_digits = 3,
                                parameter_names = c( "modelno","trial_size", "treatment_assignment_effect_size", "prognostic_factor_effect_size", 
                                                "outcome_marginal_prevalence", "prognostic_factor_prevalence" ),
                                table_colnames = c("CR", "SBR", "CAA_model", "CAA_rerand","modelno", "n", "bZ", "bX", "Pr( Y )", "Pr( X )"),
                                return_row_indices = FALSE,
                                verbose = FALSE )
{
  #' [1] Get row indices corresponding to alloc method, rerandomization type, and adjustment method
  row_indices <- list();
  row_indices[["CR"]] <- with( metric_df, which( alloc_method == "CR" & rerandomized == 0 & adjusted == get_adj_ests ));
  row_indices[["SBR"]] <- with( metric_df, which( alloc_method == "SBR" & rerandomized == 0 & adjusted == get_adj_ests ));
  row_indices[["CAA_model"]] <- with( metric_df, which( alloc_method == "CAA-MI-2-PBA-0.70" & rerandomized == 0 & adjusted == get_adj_ests ));
  row_indices[["CAA_rerand"]] <- with( metric_df, which( alloc_method == "CAA-MI-2-PBA-0.70" & rerandomized == 1 & adjusted == get_adj_ests ));

  #' [2] By (alloc_method, rerandomized, adjusted), view how many rows were selected.
  row_lengths <- sapply( row_indices, function( .indices ){ length( .indices ) })
  # Given variable row lengths, throw errors (or pad table)
  row_lengths_table <- table( row_lengths )
  if(length( row_lengths_table ) > 1 & verbose ){
    cat("WARNING: method row lengths are not identical! \nWish this warning message was more detailed...\n")
  }

  #' [3] Get statistics, round to 'round_digits'. Also get NA values.
  metrics_by_method <- lapply( row_indices, function( .indices ){
    if( length( .indices ) == 0 ){ # if no rows selected, return all NAs
      return(rep( NA, times = max( row_lengths ))) 
    }else{
      # if metric == 'power', select 'power.rerand' or 'power.pvalue' 
      #   depending on if rerandomized == TRUE or FALSE, respectively.
      if( metric == "power" ){ 
        if(any( metric_df[ .indices, "rerandomized" ] == 1 )){
          return(round( metric_df[ .indices, "power.rerand" ], round_digits ))
        }else{
          return(round( metric_df[ .indices, "power.pvalue" ], round_digits ))
        }
      }else{
        return(round( metric_df[ .indices, metric ], round_digits ))
      }
    }})
  metrics_table <- do.call( cbind, metrics_by_method )

  #' [4] Get parameters corresponding to each model.
  model_params_table <- metric_df[ row_indices[["CR"]], parameter_names ];
  
  #' [5] Piece all method components together and (2) rename column names.
  output_table <- cbind( metrics_table, model_params_table );
  dimnames( output_table )[[2]] <- table_colnames;
  
  #' [6] For diagnostics: return row indices?
  if( !return_row_indices ){
    return( summary = output_table )
  }else{
    return(list( summary = output_table,
                 row_indices = row_indices ))
  }
}
```

Here we define make_summary_tables_adj_and_unadj_sorted().
```{r summary_tables_big_and_sorted, cache = TRUE, echo = TRUE}
#' [ make_summary_tables_adj_and_unadj_sorted() ]
#' use: [1] makes summary tables (with adjusted and unadjusted estimates side by side)
#'      [2] sorts by sort_by_vars.
make_summary_tables_adj_and_unadj_sorted <- 
  function( metric_df,
            metric,
            round_digits,
            parameter_names,
            table_colnames = c("CR", "SBR", "CAA_model", "CAA_rerand", "n", "bZ", "bX", "Pr( Y )", "Pr( X )"),
            sort_by_vars = c("n", "Pr( Y )", "Pr( X )", "bZ", "bX") )
{
  #' [0] Assertions
  assert_that( sort_by_vars %in% table_colnames, 
               errmsg = "All variables in `sort_by_vars` must be in `table_colnames`." )
  assert_that( parameter_names %in% names( metric_df ), 
               errmsg = "All variables in `parameter_names` must be in data.frame `metric_df`." )
    
  #' [1] Get adjusted and unadjusted summary tables
  outdf_adj <- make_summary_table( metric_df = metric_df, metric = metric, get_adj_ests = TRUE, round_digits = round_digits,
                                   parameter_names = parameter_names, table_colnames = table_colnames )
  outdf_un <- make_summary_table( metric_df = metric_df, metric = metric, get_adj_ests = FALSE, round_digits = round_digits,
                                   parameter_names = parameter_names, table_colnames = table_colnames )
  
  #' [2] Sort rows by variables: 'sort_by_vars'
  col_indices_sort_variables <- sapply( sort_by_vars, function( .varname ){ which( table_colnames == .varname ) })
  row_indices_sorted <- do.call( order, outdf_adj[, col_indices_sort_variables ] )
  
  #' [3] Make table of [{model parameters, 'adjusted':'unadjusted' ests by randomization type.}]
  outdf_all <- cbind( modelno = outdf_adj$modelno,
                      outdf_adj[, col_indices_sort_variables ],
                      CR_adj = outdf_adj$CR, CR_un = outdf_un$CR,
                      SBR_adj = outdf_adj$SBR, SBR_un = outdf_un$SBR,
                      CAA_model_adj = outdf_adj$CAA_model, CAA_model_un = outdf_un$CAA_model,
                      CAA_rerand_adj = outdf_adj$CAA_rerand, CAA_rerand_un = outdf_un$CAA_rerand )
  
  #' [4] Exclude certain parameters. 
  col_indices_to_exclude <- which( dimnames( outdf_all)[[2]] %in% c("modelno", "CAA_rerand_un") )
  
  #' [5] Return estimates in sorted order, excluding variables in `col_indices_to_exclude`.
  return( outdf_all[ row_indices_sorted, - col_indices_to_exclude ] )
}
```

Here we define wrapper functions for each batch (aka defaults for 'parameter_names', 'table_colnames', and 'sort_by_vars').
```{r summary_table_wrapper_functions, cache = TRUE, echo = FALSE}
#' [ Define wrapper functions with defaults for 'parameter_names', 'table_colnames', and 'sort_by_vars' ]
batch1_make_summary_tables <- function( metric_df, metric ){
  return( make_summary_tables_adj_and_unadj_sorted(
    metric_df = metric_df,
    metric = metric,
    round_digits = 3,
    parameter_names =  c( "modelno","trial_size", "treatment_assignment_effect_size", "prognostic_factor_effect_size", 
                                                "outcome_marginal_prevalence", "prognostic_factor_prevalence" ),
    table_colnames = c("CR", "SBR", "CAA_model", "CAA_rerand","modelno", "n", "bZ", "bX", "Pr( Y )", "Pr( X )"),
    sort_by_vars = c("n", "Pr( Y )", "Pr( X )", "bZ", "bX")))
}

batch2_make_summary_tables <- function( metric_df, metric ){
  return( make_summary_tables_adj_and_unadj_sorted(
    metric_df = metric_df,
    metric = metric,
    round_digits = 3,
    parameter_names =  c( "modelno","trial_size", "treatment_assignment_effect_size", "prognostic_factor_effect_size", 
                                                "outcome_marginal_prevalence" ),
    table_colnames = c("CR", "SBR", "CAA_model", "CAA_rerand","modelno", "n", "bZ", "bX", "Pr( Y )"),
    sort_by_vars = c("n", "Pr( Y )", "bZ", "bX")))
}

batch3_make_summary_tables <- function( metric_df, metric ){
  return( make_summary_tables_adj_and_unadj_sorted(
    metric_df = metric_df,
    metric = metric,
    round_digits = 3,
    parameter_names =  c( "modelno","trial_size", "treatment_assignment_effect_size", "prognostic_factor_effect_size",
                          "prognostic_factor_prevalence" ),
    table_colnames = c("CR", "SBR", "CAA_model", "CAA_rerand","modelno", "n", "bZ", "bX", "Pr( X )"),
    sort_by_vars = c("n", "Pr( X )", "bZ", "bX")))
}

batch4_make_summary_tables <- function( metric_df, metric ){
  return( make_summary_tables_adj_and_unadj_sorted(
    metric_df = metric_df,
    metric = metric,
    round_digits = 3,
    parameter_names =  c( "modelno","trial_size", "treatment_assignment_effect_size", "prognostic_factor_effect_size" ),
    table_colnames = c("CR", "SBR", "CAA_model", "CAA_rerand","modelno", "n", "bZ", "bX"),
    sort_by_vars = c("n", "bZ", "bX")))
}
```

Batch 1 tables are here, but they are unformatted. 
TODO(michael): finish formatting and save to file. 
```{r batch-1-tables-unformatted, cache = TRUE, echo = FALSE, message = FALSE, warning = FALSE}
#' [ Batch 1: Binary Y, binary X ]
tbl1a <- batch1_make_summary_tables( metric_df = metrics_batch1, metric = "coverage")
tbl1b <- batch1_make_summary_tables( metric_df = metrics_batch1, metric = "bias")
tbl1c <- batch1_make_summary_tables( metric_df = metrics_batch1, metric = "power")

tbl1d <- batch1_make_summary_tables( metric_df = metrics_batch1_sub, metric = "coverage")
tbl1d_nsim <- batch1_make_summary_tables( metric_df = metrics_batch1_sub, metric = "nsim")

tbl1e <- batch1_make_summary_tables( metric_df = metrics_batch1_sub, metric = "bias")
tbl1e_nsim <- batch1_make_summary_tables( metric_df = metrics_batch1_sub, metric = "nsim")

tbl1f <- batch1_make_summary_tables( metric_df = metrics_batch1_sub, metric = "power")
tbl1f_nsim <- batch1_make_summary_tables( metric_df = metrics_batch1_sub, metric = "nsim")
```

Batch 2 tables are here, but they are unformatted. 
```{r batch-2-tables-unformatted, cache = TRUE, echo = FALSE, message = FALSE}
#' [ Batch 2: Binary Y, continuous X ]
tbl2a <- batch2_make_summary_tables( metric_df = metrics_batch2, metric = "coverage")
tbl2b <- batch2_make_summary_tables( metric_df = metrics_batch2, metric = "bias")
tbl2c <- batch2_make_summary_tables( metric_df = metrics_batch2, metric = "power")

tbl2d <- batch2_make_summary_tables( metric_df = metrics_batch2_sub, metric = "coverage")
tbl2d_nsim <- batch2_make_summary_tables( metric_df = metrics_batch2_sub, metric = "nsim")

tbl2e <- batch2_make_summary_tables( metric_df = metrics_batch2_sub, metric = "bias")
tbl2e_nsim <- batch2_make_summary_tables( metric_df = metrics_batch2_sub, metric = "nsim")

tbl2f <- batch2_make_summary_tables( metric_df = metrics_batch2_sub, metric = "power")
tbl2f_nsim <- batch2_make_summary_tables( metric_df = metrics_batch2_sub, metric = "nsim")
```

Batch 3 tables are here, but they are unformatted. 
```{r batch-3-tables-unformatted, cache = TRUE, echo = FALSE, message = FALSE}
#' [ Batch 3: Continuous Y, binary X ]
tbl3a <- batch3_make_summary_tables( metric_df = metrics_batch3, metric = "coverage")
tbl3b <- batch3_make_summary_tables( metric_df = metrics_batch3, metric = "bias")
tbl3c <- batch3_make_summary_tables( metric_df = metrics_batch3, metric = "power")
```

Batch 4 tables are here, but they are unformatted. 
```{r batch-4-tables-unformatted, cache = TRUE, echo = FALSE, message = FALSE}
#' [ Batch 4: Continuous Y, continuous X ]
tbl4a <- batch4_make_summary_tables( metric_df = metrics_batch4, metric = "coverage")
tbl4b <- batch4_make_summary_tables( metric_df = metrics_batch4, metric = "bias")
tbl4c <- batch4_make_summary_tables( metric_df = metrics_batch4, metric = "power")
```


\newpage

# Results {-}

## Batch 1: Binary outcome (Y), binary prognostic factors (X) {-}
### Complete simulation results (5010 simulations)
```{r batch-1-table-settings, cache = TRUE, echo = FALSE, results = 'asis'}
.col.names.b1 = c("n", "bZ", "bX", "Pr( Y )", "Pr( X )", "adj", "unadj", "adj", "unadj", "adj", "unadj", "adj");
.align.b1 = c(rep("c", 5), rep("r", 6), "c");
.latex_options.b1 = c("striped", "bordered", "hold_position")
.header.randomization.method.b1 = c(" " = 5, "CR" = 2, "SBR" = 2, "CAA" = 2, "CAA" = 1);
.header.analysis.method.b1 = c(" " = 5, "Model-based" = 6, "Rerandomization" = 1);
.batch.labels <- paste0("Table ", 1, c("a", "b", "c", "d", "e", "f"), 
                        ": (Binary Y, binary X) ",
                        c("Coverage probability", "Bias", "Power"))
.linesep = kable_booktabs_linesep( nlines = 6 )
```

```{r batch-1-coverage-table, cache = TRUE, echo = FALSE, results='asis'}
tbl1a[, c(-1, -dim( tbl1a )[[2]])] %>%
kable( caption = .batch.labels[ 1 ], row.names = FALSE, 
       col.names = .col.names.b1, align = .align.b1, booktabs = TRUE, linesep = .linesep) %>%
  kable_styling( latex_options = .latex_options.b1, full_width = FALSE ) %>%
  add_header_above( .header.randomization.method.b1 ) %>%
  add_header_above( .header.analysis.method.b1 )
```

\newpage
```{r batch-1-bias-table, cache = TRUE, echo = FALSE, results='asis'}
tbl1b[, c(-1, -dim( tbl1b )[[2]])] %>%
kable( caption = .batch.labels[ 2 ], row.names = FALSE, 
       col.names = .col.names.b1, align = .align.b1, booktabs = TRUE, linesep = .linesep) %>%
  kable_styling( latex_options = .latex_options.b1, full_width = FALSE ) %>%
  add_header_above( .header.randomization.method.b1 ) %>%
  add_header_above( .header.analysis.method.b1 )
```

\newpage
```{r batch-1-power-table, cache = TRUE, echo = FALSE, results='asis'}
tbl1c[, c(-1, -dim( tbl1c )[[2]])] %>%
  kable( caption = .batch.labels[ 3 ], row.names = FALSE, 
       col.names = .col.names.b1, align = .align.b1, booktabs = TRUE, linesep = .linesep) %>%
  kable_styling( latex_options = .latex_options.b1, full_width = FALSE ) %>%
  add_header_above( .header.randomization.method.b1 ) %>%
  add_header_above( .header.analysis.method.b1 )
```

\newpage
### Subsetted simulation results (simulations without non-complete separation)
```{r batch-1-subset-coverage-table, cache = TRUE, echo = FALSE, results='asis'}
#' TODO(michael 7/31): modify this subtable to include range of 'nsim' values between parameters and model estimates!
tbl1d[, c(-1, -dim( tbl1d )[[2]])] %>%
kable( caption = .batch.labels[ 4 ], row.names = FALSE, 
       col.names = .col.names.b1, align = .align.b1, booktabs = TRUE, linesep = .linesep) %>%
  kable_styling( latex_options = .latex_options.b1, full_width = FALSE ) %>%
  add_header_above( .header.randomization.method.b1 ) %>%
  add_header_above( .header.analysis.method.b1 )
```

\newpage
```{r batch-1-subset-bias-table, cache = TRUE, echo = FALSE, results='asis'}
#' TODO(michael 7/31): modify this subtable to include range of 'nsim' values between parameters and model estimates!
tbl1e[, c(-1, -dim( tbl1e )[[2]])] %>%
  kable( caption = .batch.labels[ 5 ], row.names = FALSE, 
       col.names = .col.names.b1, align = .align.b1, booktabs = TRUE, linesep = .linesep) %>%
  kable_styling( latex_options = .latex_options.b1, full_width = FALSE ) %>%
  add_header_above( .header.randomization.method.b1 ) %>%
  add_header_above( .header.analysis.method.b1 )
```

\newpage
```{r batch-1-subset-power-table, cache = TRUE, echo = FALSE, results='asis'}
tbl1f[, c(-1, -dim( tbl1f )[[2]])] %>%
  kable( caption = .batch.labels[ 6 ], row.names = FALSE, 
       col.names = .col.names.b1, align = .align.b1, booktabs = TRUE, linesep = .linesep) %>%
  kable_styling( latex_options = .latex_options.b1, full_width = FALSE ) %>%
  add_header_above( .header.randomization.method.b1 ) %>%
  add_header_above( .header.analysis.method.b1 )
```


\newpage
## Batch 2: Binary outcome (Y), continuous prognostic factors (X) {-}
```{r batch-2-table-settings, cache = TRUE, echo = FALSE, results = 'asis'}
.col.names.b2 = c("n", "exp( bZ )", "exp( bX )", "Pr( Y )", "adj", "unadj", "adj", "unadj", "adj", "unadj", "adj");
.align.b2 = c(rep("c", 4), rep("r", 6), "c");
.latex_options.b2 = c("striped", "bordered", "hold_position")
.header.randomization.method.b2 = c(" " = 4, "CR" = 2, "SBR" = 2, "CAA" = 2, "CAA" = 1);
.header.analysis.method.b2 = c(" " = 4, "Model-based" = 6, "Rerandomization" = 1);

.batch.labels <- paste0("Table ", 2, c("a", "b", "c", "d", "e", "f"), 
                        ": (Binary Y, continuous X) ",
                        c("Coverage probability", "Bias", "Power"))

.linesep = kable_booktabs_linesep( nlines = 6 )
```

### Complete simulation results (5010 simulations)
```{r batch-2-coverage-table, cache = TRUE, echo = FALSE, results='asis'}
tbl2a[, c(-1, -dim( tbl2a )[[2]])] %>%
kable( caption = .batch.labels[ 1 ], row.names = FALSE, 
       col.names = .col.names.b2, align = .align.b2, booktabs = TRUE, linesep = .linesep) %>%
  kable_styling( latex_options = .latex_options.b2, full_width = FALSE ) %>%
  add_header_above( .header.randomization.method.b2 ) %>%
  add_header_above( .header.analysis.method.b2 )
```

\newpage
```{r batch-2-bias-table, cache = TRUE, echo = FALSE, results='asis'}
tbl2b[, c(-1, -dim( tbl2b )[[2]])] %>%
  kable( caption = .batch.labels[ 2 ], row.names = FALSE, 
       col.names = .col.names.b2, align = .align.b2, booktabs = TRUE, linesep = .linesep) %>%
  kable_styling( latex_options = .latex_options.b2, full_width = FALSE ) %>%
  add_header_above( .header.randomization.method.b2 ) %>%
  add_header_above( .header.analysis.method.b2 )
```

\newpage
```{r batch-2-power-table, cache = TRUE, echo = FALSE, results='asis'}
tbl2c[, c(-1, -dim( tbl2c )[[2]])] %>%
  kable( caption = .batch.labels[ 3 ], row.names = FALSE, 
       col.names = .col.names.b2, align = .align.b2, booktabs = TRUE, linesep = .linesep) %>%
  kable_styling( latex_options = .latex_options.b2, full_width = FALSE ) %>%
  add_header_above( .header.randomization.method.b2 ) %>%
  add_header_above( .header.analysis.method.b2 )
```

\newpage
### Subsetted simulation results (simulations without non-complete separation)
```{r batch-2-subset-coverage-table, cache = TRUE, echo = FALSE, results='asis'}
tbl2d[, c(-1, -dim( tbl2d )[[2]])] %>%
  kable( caption = .batch.labels[ 4 ], row.names = FALSE, 
       col.names = .col.names.b2, align = .align.b2, booktabs = TRUE, linesep = .linesep) %>%
  kable_styling( latex_options = .latex_options.b2, full_width = FALSE ) %>%
  add_header_above( .header.randomization.method.b2 ) %>%
  add_header_above( .header.analysis.method.b2 )
```

\newpage
```{r batch-2-subset-bias-table, cache = TRUE, echo = FALSE, results='asis'}
tbl2e[, c(-1, -dim( tbl2e )[[2]])] %>%
  kable( caption = .batch.labels[ 5 ], row.names = FALSE, 
       col.names = .col.names.b2, align = .align.b2, booktabs = TRUE, linesep = .linesep) %>%
  kable_styling( latex_options = .latex_options.b2, full_width = FALSE ) %>%
  add_header_above( .header.randomization.method.b2 ) %>%
  add_header_above( .header.analysis.method.b2 )
```

\newpage
```{r batch-2-subset-power-table, cache = TRUE, echo = FALSE, results='asis'}
tbl2f[, c(-1, -dim( tbl2f )[[2]])] %>%
  kable( caption = .batch.labels[ 6 ], row.names = FALSE, 
       col.names = .col.names.b2, align = .align.b2, booktabs = TRUE, linesep = .linesep) %>%
  kable_styling( latex_options = .latex_options.b2, full_width = FALSE ) %>%
  add_header_above( .header.randomization.method.b2 ) %>%
  add_header_above( .header.analysis.method.b2 )
```


```{r batch-3-table-settings, cache = TRUE, echo = FALSE, results = 'asis'}
.col.names.b3 = c("n", "exp( bZ )", "exp( bX )", "Pr( X )", "adj", "unadj", "adj", "unadj", "adj", "unadj", "adj");
.align.b3 = c(rep("c", 4), rep("r", 6), "c");
.latex_options.b3 = c("striped", "bordered", "hold_position")
.header.randomization.method.b3 = c(" " = 4, "CR" = 2, "SBR" = 2, "CAA" = 2, "CAA" = 1);
.header.analysis.method.b3 = c(" " = 4, "Model-based" = 6, "Rerandomization" = 1);

.batch.labels <- paste0("Table ", 3, c("a", "b", "c", "d", "e", "f"), 
                        ": (Continuous Y, binary X) ",
                        c("Coverage probability", "Bias", "Power"))
.linesep = kable_booktabs_linesep( nlines = 6 )
```

\newpage
## Batch 3: Continuous outcome (Y), binary prognostic factors (X) {-}
```{r batch-3-coverage-table, cache = TRUE, echo = FALSE, results='asis'}
tbl3a[, c(-1, -dim( tbl3a )[[2]])] %>%
  kable( caption = .batch.labels[ 1 ], row.names = FALSE, 
       col.names = .col.names.b3, align = .align.b3, booktabs = TRUE, linesep = .linesep) %>%
  kable_styling( latex_options = .latex_options.b3, full_width = FALSE ) %>%
  add_header_above( .header.randomization.method.b3 ) %>%
  add_header_above( .header.analysis.method.b3 )
```

\newpage
```{r batch-3-bias-table, cache = TRUE, echo = FALSE, results='asis'}
tbl3b[, c(-1, -dim( tbl3b )[[2]])] %>%
  kable( caption = .batch.labels[ 2 ], row.names = FALSE, 
       col.names = .col.names.b3, align = .align.b3, booktabs = TRUE, linesep = .linesep) %>%
  kable_styling( latex_options = .latex_options.b3, full_width = FALSE ) %>%
  add_header_above( .header.randomization.method.b3 ) %>%
  add_header_above( .header.analysis.method.b3 )
```

\newpage
```{r batch-3-power-table, cache = TRUE, echo = FALSE, results='asis'}
tbl3c[, c(-1, -dim( tbl3c )[[2]])] %>%
kable( caption = .batch.labels[ 3 ], row.names = FALSE, 
       col.names = .col.names.b3, align = .align.b3, booktabs = TRUE, linesep = .linesep) %>%
  kable_styling( latex_options = .latex_options.b3, full_width = FALSE ) %>%
  add_header_above( .header.randomization.method.b3 ) %>%
  add_header_above( .header.analysis.method.b3 )
```



```{r batch-4-table-settings, cache = TRUE, echo = FALSE, results = 'asis'}
.col.names.b4 = c("n", "exp( bZ )", "exp( bX )", "adj", "unadj", "adj", "unadj", "adj", "unadj", "adj");
.align.b4 = c(rep("c", 3), rep("r", 6), "c");
.latex_options.b4 = c("striped", "bordered", "hold_position");
.header.randomization.method.b4 = c(" " = 3, "CR" = 2, "SBR" = 2, "CAA" = 2, "CAA" = 1);
.header.analysis.method.b4 = c(" " = 3, "Model-based" = 6, "Rerandomization" = 1);

.batch.labels <- paste0("Table ", 4, c("a", "b", "c", "d", "e", "f"), 
                        ": (Continuous Y, continuous X) ",
                        c("Coverage probability", "Bias", "Power"))
.linesep = kable_booktabs_linesep( nlines = 6 )
```

\newpage
## Batch 4: Continuous outcome (Y), continuous prognostic factors (X) {-}
```{r batch-4-coverage-table, cache = TRUE, echo = FALSE, results='asis'}
tbl4a[, c(-1, -dim( tbl4a )[[2]])] %>%
kable( caption = .batch.labels[ 1 ], row.names = FALSE, 
       col.names = .col.names.b4, align = .align.b4, booktabs = TRUE, linesep = .linesep ) %>%
  kable_styling( latex_options = .latex_options.b4, full_width = FALSE ) %>%
  add_header_above( .header.randomization.method.b4 ) %>%
  add_header_above( .header.analysis.method.b4 )
```

\newpage
```{r batch-4-bias-table, cache = TRUE, echo = FALSE, results='asis'}
tbl4b[, c(-1, -dim( tbl4b )[[2]])] %>%
kable( caption = .batch.labels[ 2 ], row.names = FALSE, 
       col.names = .col.names.b4, align = .align.b4, booktabs = TRUE, linesep = .linesep) %>%
  kable_styling( latex_options = .latex_options.b4, full_width = FALSE ) %>%
  add_header_above( .header.randomization.method.b4 ) %>%
  add_header_above( .header.analysis.method.b4 )
```

\newpage
```{r batch-4-power-table, cache = TRUE, echo = FALSE, results='asis'}
tbl4c[, c(-1, -dim( tbl4c )[[2]])] %>%
kable( caption = .batch.labels[ 3 ], row.names = FALSE, 
       col.names = .col.names.b4, align = .align.b4, booktabs = TRUE, linesep = .linesep) %>%
  kable_styling( latex_options = .latex_options.b4, full_width = FALSE ) %>%
  add_header_above( .header.randomization.method.b4 ) %>%
  add_header_above( .header.analysis.method.b4 )
```

